Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-28 salmon/paper/salmon_paper.Rmd
paper update

dat$col = as.numeric(as.factor(dat$species))
ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = species), position = "stack") +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  scale_fill_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
    labels =c("Chinook","Sockeye","Coho","Pink","Chum")) + 
  facet_wrap(~region, scale="free_y")
```

>>>>

dat$col = as.numeric(as.factor(dat$species))
g1 = ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = species), position = "stack") +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  scale_fill_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
    labels =c("Chinook","Sockeye","Coho","Pink","Chum")) + 
  facet_wrap(~region, scale="free_y")

# bring in total harvest data (hatchery + wild)
hatch = read.csv("salmon/data-generated/commonPropertyCommercialCatch.csv")
hatch = hatch[,c("Year","Chinook","Sockeye","Coho","Pink","Chum","Region")]
hatch$Region = as.character(hatch$Region)
hatch$Region[which(hatch$Region=="PWS")] = "Prince William Sound"
hatch = melt(hatch, id.vars = c("Year","Region"))
names(hatch)[which(names(hatch)=="variable")]="Species"

g2 = ggplot(hatch, aes(Year, value, color=Species)) + 
  geom_line() + facet_wrap(~Region) + 
  xlab("Year") + ylab("Hatchery contribution to catch (%)") + 
  scale_color_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
    labels =c("Chinook","Sockeye","Coho","Pink","Chum"))

gridExtra::grid.arrange(g1, g2)
